Manual classification of tumor cells

### 2024-05-16 analyses/cell-type-ewings/template_notebooks/01-marker-genes.Rmd
update documentation

classifications_filename <- glue::glue("{params$library_id}_tumor_normal_classifications.tsv")
output_classifications_file <- file.path(params$results_dir, classifications_filename)
```

@@

### Compare with SingleR and CellAssign classifictions

>>>>

classifications_filename <- glue::glue("{params$library_id}_tumor-normal-classifications.tsv")
output_classifications_file <- file.path(params$results_dir, classifications_filename)
```

@@

### Compare with SingleR and CellAssign classifications
